---
title: "Simulated example"
author: "Sreenath Madathil"
date: "April 8, 2018"
output: html_document
---

Excess relative risk estimated using Odds ratios as suggested by [David B. Richardson, Jay S. Kaufman,American Journal of  Epidemiology,2010](https://doi.org/10.1093/aje/kwn411). [Haitao Chu, Stephen R Cole](https://insights.ovid.com/pubmed?pmid=21228700) proposed Bayesian approach to the model for two binary exposures.   

Briefly the model is, 
$$odds_{i} = exp(\alpha)*(1+\beta_{1}*x_{1,i} + \beta_{2}*x_{2,i} + \beta_{3}*x_{1,i}*x_{2,i})$$  
$$P(y_{i} = 1) = \frac{odds_{i}}{1+odds_{i}}$$  

With the following constrains on parameters
$$ \beta_{1} , \beta_{2} >= -1 $$  
$$ \beta_{3} >= -(1+\beta_{1} + \beta_{2})$$


###Simulating data
```{r, echo=FALSE, warning=FALSE,results='hide',message=FALSE}
setwd("S://sareku/Public_Git_Repos/Linear_Excess_Risk_Model/")
library(rstan)
options(mc.cores = parallel::detectCores())
rstan_options(auto_write = TRUE)
library(bayesplot)
library(ggplot2)
library(jagsUI)
```

```{r}
set.seed(4507907)

N <- 4000
x1 <- rbinom(N,1,0.5)
x2 <- rbinom(N,1,0.5)
x1x2 <- x1*x2

b <- c(-1,2,2,-1)

odds <- exp(b[1])*(1+ b[2]*x1 + b[3]*x2 + b[4]*x1x2)
p <- odds/(1+odds)

y <- rbinom(N,1,p)

dat = list(N=N, A=x1,B=x2, y=y)

```

###Model specification in Stan
```{r}
writeLines(readLines("linOdds.stan"))
```
###Fitting model in stan
```{r,results='hide',warning=FALSE, message=FALSE}
fit <- stan("S:/sareku/DATAs/RStan/linearExcess risk model/linOdds.stan",
            data=dat, control = list(adapt_delta=0.99, max_treedepth=14))
```
###Examining results
```{r, warning=FALSE, message=FALSE}
pairs(fit, pars=c("b0","b1","b2","b3"))

mcmc_trace(as.array(fit), pars=c("b0","b1","b2","b3"))

print(fit, pars=c("b0","b1","b2","b3"))

mcmc_areas(as.array(fit), pars=c("b1","b2","b3"),
           point_est ="median", prob=0.8)+
  ggplot2::geom_vline(xintercept=b[2:4])

```
###Posterior predicitive check
```{r}
yrep <- rstan::extract(fit, pars="yrep")
prep <- rstan::extract(fit, pars="pr")
odrep <- rstan::extract(fit, pars="odds")
ppc_bars(y,yrep$yrep[1:1000,])
ppc_dens_overlay(p,prep$pr[1:1000,])
ppc_intervals(odds, odrep$odds[1:1000,])
```

###Fitting model in Jags
```{r}
jD <- list(N=N, A=x1, B=x2, y=y, one=1)
js <- jags(data=dat, model.file ="linodds.jags", 
           parameters.to.save =c("b0","b1","b2","b3"),
           n.iter=10000, n.burnin =5000, parallel = TRUE,
           n.chains =4)

js

mcmc_trace(js$sample, pars=c("b0","b1","b2","b3"))
mcmc_areas(js$sample, pars=c("b1","b2","b3"), prob=0.8)+geom_vline(xintercept =b[2:4])

```

###Finding
The 80\% credible intervals of estimates include the true parameter values. 
